---
title: Genetic Associations with Survival Outcomes after Matched Unrelated Donor
  Allogeneic Hematopoietic Stem Cell Transplantation
author: "Ezgi Karaesmen"
documentclass: DissertateOSU
output:
  pdf_document:  
    includes:
      in_header: preamble.tex
    keep_tex: yes
    latex_engine: xelatex  
    number_sections: true  
header-includes:
- \usepackage{booktabs}
- \usepackage{placeins}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{tabulary}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{amsrefs}
- \usepackage{filecontents}
- \usepackage{afterpage}
- \usepackage[graphicx]{realboxes}
- \usepackage{rotating}
- \usepackage{lscape}
- \usepackage{adjustbox}
- \usepackage{caption}
- \usepackage{geometry}
- \usepackage{makecell}

link-citations: yes
geometry:
- top=1in
- bottom=1in
- right=1in
- left=1.5in
- includefoot
params:
  committee1: Lara E Sucheston-Campbell, PhD, Advisor
  committee2: Kellie Archer, PhD
  committee3: Moray Campbell, PhD
  committee4: Daniel Kinnamon, PhD
  degree: Pharmaceutical Sciences
  gradschool: The Ohio State University
  year: '2020'
bibliography: dissertation_references.bib
editor_options: 
  chunk_output_type: console
---

```{r global_options, include=FALSE}
## This saves you from having to do this for every chunk
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache=FALSE,
                      tidy=TRUE,
                      tidy.opts=list(width.cutoff=45))

## Do NOT Remove
library(tidyverse)
library(formatR)
library(kableExtra)
library(dissertateUSU)
#dissertateUSU::preamble_for_title()
```

<!-- Title page printed automatically -->
\pagenumbering{roman}
\pagestyle{empty}
\copyrightpage

<!-- Abstract -->
\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter*{ABSTRACT}
\addcontentsline{toc}{section}{Abstract}
\doublespacing

```{r child = "abstract.Rmd"}
```


<!-- Dedication -->
\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
<!-- \chapter*{DEDICATION} -->
\addcontentsline{toc}{section}{Dedication}

\vspace*{\fill}
  \begin{center}
	\doublespacing
	This is dedicated to Abbas, \\
	my parents, grandparents and brother \\
	for their endless love and support, \\
	to all the friends from all around the world \\
	for making this journey worthwhile and enjoyable, \\
	and to my sweet little bundle of joy Bernie \\
	for always being by my side.
  \end{center}
\vspace*{\fill}


<!-- Acknowledgements -->
\newpage
\pagestyle{plain} 
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{section}{Acknowledgments}

\doublespacing

```{r child = "acknowledgements.Rmd"}
```


<!-- Vita -->
\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter*{VITA}
\addcontentsline{toc}{section}{Vita}
\singlespacing

```{r child = "vita.Rmd"}
```


<!-- Front Matter -->
\newpage
\pagestyle{plain} 
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\tableofcontents

\newpage
\pagestyle{plain} 
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\listoftables

\newpage
\pagestyle{plain} 
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\listoffigures

\newpage
\pagenumbering{arabic}

<!-- Introduction -->
\newpage
\pagestyle{plain} 
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter{Introduction}
\doublespacing

```{r child = "chapter1.Rmd"}
```

\FloatBarrier

<!-- Chapter 2 -->
\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter{Replication and Validation of Previous HSCT Literature}
\doublespacing

```{r child = "chapter2.Rmd"}
```

\FloatBarrier

<!-- Chapter 3 -->
\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter{IL1RL1 variants as biomarker for GVHD and infection deaths following transplant.}
\doublespacing

```{r child = "chapter3.Rmd"}
```

\FloatBarrier

<!-- Chapter 4 -->

\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter{Genome Wide Interaction Analysis of Conditioning Regimen Intensity with Overall Survival after HSCT}
\doublespacing

```{r child="chapter4.Rmd", eval=TRUE}
```


\FloatBarrier

<!-- Chapter 5 -->

\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\chapter{Construction of DISCOVeRY-BMT GWAS Results Database}
\doublespacing
```{r child = "chapter5.Rmd", eval=TRUE}
```



\FloatBarrier

<!-- Chapter 6 -->

\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}

\chapter{Conclusion}

\doublespacing

```{r child = "conclusion.Rmd", eval=TRUE}
```


\FloatBarrier

\newpage
\pagestyle{plain}
\fancyhead[L]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}


\chapter*{REFERENCES}
\singlespacing
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.4in}
\setlength{\parskip}{12pt}

<div id="refs"></div>

\FloatBarrier

<!-- \newpage -->

<!-- \pagestyle{plain} -->
<!-- \fancyhead[L]{} -->
<!-- \fancyhead[R]{} -->
<!-- \fancyfoot[C]{\thepage} -->
<!-- \chapter*{APPENDICES} -->
<!-- \addcontentsline{toc}{chapter}{APPENDICES} -->

<!-- \doublespacing  -->
<!-- \setlength{\parindent}{0.4in} -->
<!-- \setlength{\leftskip}{0in} -->
<!-- \setlength{\parskip}{12pt} -->

<!-- ```{r child="ch2_appendix.Rmd", eval=TRUE} -->
<!-- ``` -->


